% -*-coding: utf-8 -*-

\zp{Ironic}{Alanis Morisette}

\zs
An \Ch{F#}{old} \Ch{H}{man} \Ch{F#}{turned} ninety-\Ch{G#mi}{eight}.
He won the lottery and died the next day

It's a black fly in your chardonnay.
It's a death row pardon two minutes too late

Isn't it \Ch{F#}{ironic?}\Ch{H}{} Don't you \Ch{F#}{think} \Ch{G#mi}{}
\ks

\zr
It's like \Ch{F#}{ra}\Ch{H}{in} on your \Ch{F#}{wedding} \Ch{G#mi}{day.}
It's a free \Ch{F#}{ri}\Ch{H}{de} when you've \Ch{F#}{already} \Ch{G#mi}{paid}

It's the good ad\Ch{F#}{vi}\Ch{H}{ce} that you \Ch{F#}{just} didn't \Ch{G#mi}{take}

\Ch{A}{And} who would have \Ch{G#mi}{thought}... it \Ch{F#}{figures}
\kr

\zs
Mr. Play-it-safe was afraid to fly

He packed his suitcase and kissed his kids good-bye

He waited his whole damn life just to take that flight

And as the plane crashed down he thought ``Well isn't this nice...''

And isn't it ironic? Don't you think?
\ks

\zr  \kr

\zs
Well, \Ch{H}{life} has a funny way of sneaking \Ch{F#}{up} on you

When you think everything is okay and \Ch{G#mi}{everything's} going right

And \Ch{H}{life} has a funny way of helping \Ch{F#}{you} out when

You think everything's gone wrong and \Ch{G#mi}{everything} blows up in your face
\ks

\zs
A traffic jam when you are already late

A no-smoking sign on your cigarette break

It's like ten thousand spoons when all you need is a knife

It's like meeting the man of my dreams then meeting his beautiful wife

And isn't it ironic? Don't you think?

A little too ironic. And yeah I really do think
\ks

\zr  \kr

\zs
\Ch{H}{Life} has a funny way of sneaking up on \Ch{F#}{you}

\Ch{H}{Life} has a funny, funny way \Ch{F#}{of} helping you \Ch{H}{out}, helping you out
\ks

\kp






















