\zp{Father and son}{Cat Stevents}


Father
\zs
It's not \Ch{G}{time} to make a \Ch{D}{change}, just \Ch{C}{relax}, take it \Ch{Am7}{easy}.

You're still \Ch{G}{young}, that's your \Ch{Em}{fault}, there's so \Ch{Am}{much} you have to \Ch{D}{know}.

Find a \Ch{G}{girl}, settle \Ch{D}{down}, if you \Ch{C}{want} you can \Ch{Am7}{marry}.

Look at \Ch{G}{me}, I am \Ch{Em}{old}, but I'm \Ch{Am}{happy}.\Ch{C}{} ~ \Ch{D}{}
\ks

\zs
I was \Ch{G}{once} like you are \Ch{Bm7}{now}, and I \Ch{C}{know} that it's not \Ch{Am7}{easy},

To be \Ch{G}{calm} when you've \Ch{Em}{found} something going \Ch{Am}{on}. \Ch{C}{} ~ \Ch{D}{}

But take your \Ch{G}{time}, think a \Ch{Bm7}{lot}, think \Ch{C}{of} everything you'\Ch{Am7}{ve got}.

For you will \Ch{G}{still} be here to\Ch{Em}{morrow}, but your \Ch{D}{dreams} may \Ch{G}{not}. \Ch{G/C}{(riff)}, \Ch{G/C}{(riff)}
\ks

Son
\zs
How can \Ch{G}{I} try to \Ch{Bm}{explain}, when I \Ch{C}{do} he turns away ag\Ch{Am7}{ain.}

It's \Ch{G}{always} been the \Ch{Em}{same}, same old \Ch{Am}{story}. \Ch{C}{} ~ \Ch{D}{}

From the \Ch{G}{moment} I could \Ch{Bm}{talk} I was \Ch{C}{ordered} to \Ch{Am7}{listen}.

Now there's a \Ch{G}{way} and I \Ch{Em}{know} that I \Ch{D}{have} to \Ch{G}{go} away.

I \Ch{D}{know} I \Ch{C}{have} to \Ch{G}{go}. \Ch{G/C}{(riff)} \Ch{G/C}{(riff)}\\
\ks

Father
\zs
It's not time to make a change, just sit down, take it slowly.

You're still young, that's your fault, there's so much you have to go through.

Find a girl, settle down, if you want you can marry. 

Look at me, I am old, but I'm happy.
\ks

Son
\zs
All the times that I cried, keeping all the things I knew inside, 

It's hard, but it's harder to ignore it.

If they were right, I'd agree, but it's them, they know not me.

Now there's a way and I know that I have to go away. I know I have to go.
\ks

\kp
