\zp{Johnny B Goode}{Chuck Berry}

\ifdefined TPBAND
<G> <C> <D>

\zs
Deep down Louisiana close to New Orleans

Way back up in the woods among the ever greens

There stood a log cabin made of earth and wood

Where lived a country boy named Johnny B Goode

Who never ever learned to read or write so well

But he could play the guitar just like a ringing a bell
\ks

\zr
Go, go! Go, Johnny, go, go!

Go, Johnny, go, go! Go, Johnny, go, go!

Go, Johnny, go, go! Johnny B Goode
\kr
\else
\zs
<G>Deep down Louisiana close to New Orleans

Way back up in the woods among the ever greens

There <C>stood a log cabin made of earth and wood

Where <G>lived a country boy named Johnny B Goode

Who <D>never ever learned to read or write so well

But he could <G>play the guitar just like a ringing a bell
\ks

\zr
<G>Go, go! Go, Johnny, go, go!

Go, Johnny, go, <C>go! Go, Johnny, go, <G>go!

Go, Johnny, go, <D>go! Johnny B <G>Goode
\kr
\fi

\zs
He used to carry his guitar in a gunny sack

Go sit beneath the tree by the railroad track

Oh, the engineers would see him sitting in the shade

Strumming with the rhythm that the drivers made

People passing by they would stop and say

Oh my that little country boy could play
\ks

\zr\kr

\zs (solo) \ks 

\zs
His mother told him: ``Someday you will be a man

And you will be the leader of a big old band

Many people coming from miles around

To hear you play your music when the sun go down

Maybe someday your name will be in lights

Saying `Johnny B Goode' tonight.''
\ks

\zr\kr

\ifdefined TPBAND
<G> <G7> <C> <Cm> <D> <G>
\fi
\kp
