% -*-coding: utf-8 -*-

\zp{Hotel California}{Eagles}

\Ch{Hmi}{} \Ch{F#}{} \Ch{A}{} \Ch{E}{} \Ch{G}{} \Ch{D}{} \Ch{Emi}{} \Ch{F#}{}

\zs
\Ch{Hmi}{On a} dark desert highway,
\Ch{F#}{cool} wind in my hair,

\Ch{A}{Warm} smell of colitas
\Ch{E}{rising} up through the air.

\Ch{G}{Up} a head in the distance,
I \Ch{D}{saw} a shimmering light

My \Ch{Emi}{head} grew heavy and my sight grew dim,
I \Ch{F#}{had} to stop for the night
\ks

\zs
There she stood in the doorway
I heard the mission bell

And I was thinking to myself
this could be heaven or this could be hell

Then she lit up a candle
And she showed me the way

There were voices down the corridor
I thought I heard them say:
\ks

\zr
\Ch{G}{Welcome} to the Hotel Cali\Ch{D}{fornia}.

Such a \Ch{Emi}{lovely} place (such a lovely place),
such a \Ch{Hmi7}{lovely} face.

\Ch{G}{Plenty} of room at the Hotel \Ch{D}{California}.

Any \Ch{Emi}{time} of year (any time of year),
you can \Ch{F#}{find} it here.
\kr

\zs
Her mind is Tiffany twisted,
she got a Mercedes Benz,

she got a lot of pretty,
pretty boys that she calls friends,

How they dance in the courtyard
sweet summer sweat.

Some dance to remember
some dance to forget.
\ks

\zs
So I called up the captain:
Please bring me more wine

We haven't had that spirit
here since nineteen sixty-nine.

And still those voices are calling from far away

wake you up in the middle of the night
just to hear them say:
\ks

\zr
Welcome to the Hotel California.

Such a lovely place (such a lovely place),
such a lovely face.

They livin'it up at the Hotel California.

What a nice surprise (what a nice surprise),
bring your alibis.
\kr

\zs
Mirrors on the ceiling,
The pink champagne on ice, (and she said,)

\uv{We are all just prisoners here of our own device.}

And in the master's chambers
They gathered for the feast,

They stab it with their steely knives,
but they can't kill the beast.
\ks

\zs
Last thing I remember,
I was running for the door

I had to find the passage
back to the place I was before.

Relax, said the night man,
we are programmed to receive

You can check out any time you like,
but you can never leave.
\ks

\kp






















