% -*-coding: utf-8 -*-

\zp{Summertime}{Mungo Jerry}

Intro:  
| E – E | E – E | A – A | E – E | B – A | E – E | 

\zs
In the \Ch{E}{summertime} when the weather is high,
                              
you can stretch right up and touch the sky,

when the \Ch{A}{weather} is fine, you got women, you got women on your \Ch{E}{mind.}        

Have a \Ch{B}{drink,} have a drive, 

\Ch{A}{go out} and see what you can \Ch{E}{find.}
\ks

\zs
If her daddy's rich, take her out for a meal,
                           
if her daddy's poor, just do as you feel.

Speed along the lane, do a ton or a ton and twenty-five.
         
When the sun goes down,   

you can make it make it good in a lay-by.
\ks

\zs
We're not grey people, we're not dirty, we're not mean,
                             
we love everybody but we do as we please.

When the weather is fine, we go fishing or go swimming in the sea.      

We're always happy,

life's for living, yeah, that's our philosophy.
\ks

\zs
Sing along with us, da da di di di 
                       
Da da da da yeah we’re happy 

Da da da da, di di di di di da da da 

Da da da da , 

da da da da da da da da da da da da 
\ks

piano solo 
| E – E | E – E | A – A | E – E | B – A | E – E | 


\zs
When the winter's here, yeah, it's party-time, 
                                                       
bring a bottle, wear your bright clothes, it'll soon be summertime.

And we'll sing again, we'll go driving or maybe we'll settle down.    
                
If she's rich if she's nice, 

bring your friend and we will all go into town.
\ks

\kp