% -*-coding: utf-8 -*-

\zp{Fuking Perfect}{Pink}

\zs
 Made a \Ch{G}{wrong} turn, once \Ch{Dsus}{or twice}. Dug my \Ch{Em7}{way} out, blood and \Ch{Cadd9}{fire}

Bad \Ch{G}{decisions}. That's \Ch{Dsus}{alright}, welcome \Ch{Em7}{to my} silly \Ch{Cadd9}{life}

\Ch{G}{Mistreated}, misplaced, missundaz\Ch{Dsus}{tood}. Miss "no way it's all \Ch{Em7}{good}"

It didn't slow me \Ch{Cadd9}{down}. \Ch{G}{Mistaken}. Always second guess\Ch{Dsus}{ing}

Underestimat\Ch{Em7}{ed}, look, I'm still aro\Ch{Cadd9}{und}
\ks

\zr
\Ch{G}{Pretty}, pretty please. Don't you \Ch{Dsus}{ever, ever} feel

Like your \Ch{Em7}{less than}, fuckin' per\Ch{Cadd9}{fect}

\Ch{G}{Pretty}, pretty please, if you \Ch{Dsus}{ever, ever} feel

Like your no\Ch{Em7}{thing}, you're fuckin \Ch{Cadd9}{perfect} to me
\kr

\zs
You're so mean. When you talk about yourself. You are wrong. 

Change the voices in your head. Make them like you instead.

So complicated. Look happy you'll make it. Filled with so much hatred. Such a tired game

It's enough. I've done all I can think of. Chased down all my demons. See you do the same
\ks

\zr
\kr

\zs
\Ch{G}{The} whole world's scare so I swallow the fear

\Ch{Dsus}{The} only thing I should be drinking is an ice cold beer

\Ch{Em7}So cool in line and we try, try, try

\Ch{Cadd9}But we try too hard, it's a waste of my time

\Ch{G}{Done} looking for critics, cuz they're everywhere

\Ch{Dsus}{They} don't like me jeans, they don't get my hair

\Ch{Em7}{Exchange} ourselves and we do it all the time

\Ch{Cadd9}{Why} do we do that

Why do I do that

Why do I do that
\ks

\zr \kr

\kp