% -*-coding: utf-8 -*-

\zp{Mother}{Pink Floyd}
\zs
\Ch{G}{Mother,} do you think they'll drop the \Ch{C}{bomb?} \Ch{D}{} \Ch{G}{}

\Ch{G}{Mother,} do you think they'll like this \Ch{C}{song?} \Ch{D}{} \Ch{G}{} 

\Ch{C}{Mother,}  do you think they'll try to break my \Ch{G}{balls?}

\Ch{D}{Ohhhh}..   \Ch{C}{Ahhhh}.. Mother, should I build a \Ch{G}{wall?}
\ks

\zs
Mother, should I run for president?

Mother, should I trust the government?

Mother, will they put me in the firing line?

Ohhhh...  Ahhhhh.. Is it just a waste of time?
\ks

\zr
\Ch{G}{Hush} now, baby, don't you \Ch{C}{cry}

\Ch{F}{Mama}'s gonna make all of your \Ch{C}{nightmares} come true

\Ch{F}{Mama}'s gonna put all of her \Ch{C}{fears} into you

\Ch{F}{Mama}'s gonna keep you right here, \Ch{C}{under} her wing

\Ch{F}{She} won't let you fly, but she \Ch{C}{might} let you sing

\Ch{F}{Mama}'s gonna keep baby \Ch{C}{cozy} and \Ch{G}{warm}

\Ch{D}{Ohhhh}...  \Ch{C}{Babe}

\Ch{D}{Ohhhh}...  \Ch{C}{Babe}

\Ch{D}{Ohh}... Babe, \Ch{C}{of} course mama's gonna help build the \Ch{G}{wall}
\kr

\zs
Mother, do you think she's good enough for me?

Mother, do you think she's dangerous to me?

Mother, will she tear your little boy apart?

Oohhhh... Aaahhh... Mother, will she break my heart?
\ks

\zr
Hush now, baby, don't you cry

Mama's gonna check out all of your girlfriends for you

Mama won't let anyone dirty get through

Mama's gonna wait up until you get in

Mama will always find out just where you've been

Mama's gonna keep baby healthy and clean

Ooohhhh...  Baby

Ooohhhh...  Baby

Ooohhhh baby, you'll always be baby to me

\Ch{G}{Mother,} did it need to be so \Ch{C}{high}?
\kr

\kp

