% -*-coding: utf-8 -*-

\zp{Shine on your crazy diamond}{Pink Floyd}

\zs
\Ch{Gmi}{Remember} when you were young,
\Ch{F#}{you} shone like the \Ch{B}{sun}.

\Ch{Es}{Shine} \Ch{Es/D}{on} you \Ch{Cmi}{cr} \Ch{Cmi/Bb}{azy} di\Ch{F}{amond}.

\Ch{Gmi}{Now} there's a look in your eyes
\Ch{F#}{like} black holes in the \Ch{B}{sky}.

\Ch{Es}{Shine} \Ch{Es/D}{on} you \Ch{Cmi}{cr} \Ch{Cmi/Bb}{azy} di\Ch{F}{amond}.

You were \Ch{Gmi}{caught} in the crossfire
\Ch{Gmmaj7/F#}{of} childhood and stardom,

\Ch{Gm7/F}{Blown} on the steel \Ch{C9}{breeze}.

\Ch{Es}{Come} on you target for \Ch{Edimi}{faraway} laughter,

\Ch{B/F}{Come} on you stranger, you \Ch{Dmi}{legend}, you \Ch{D7}{martyr}, and \Ch{Gmi}{shine}!
\ks

\Ch{F#}{} \Ch{Bb}{} \Ch{E}{} \Ch{Eb/D}{} \Ch{Cmi}{} \Ch{Cmi/Bb}{} \Ch{F}{}

\zs
You reached for the secret too soon,
you cried for the moon.

Shine on you crazy diamond.

Threatened by shadows at night
and exposed in the light.

Shine on you crazy diamond.

Well you wore out your welcome
With random precision,

Rode on the steel breeze.

Come on you raver, you seer of visions,

Come on you painter, you piper, you prisoner, and shine!
\ks

\zs
Nobody knows where you are,
How near or how far.

Shine on you crazy diamond.

Pile on many more layers,
And I'll be joining you there.

Shine on you crazy diamond.

And we'll bask in the shadow of yesterday's triumph,
Sail on the steel breeze.

Come on you boy child, you winner and loser,

Come on you miner for truth and delusion and shine!
\ks

\kp





