% -*-coding: utf-8 -*-

\zp{Comfortably Numb}{Pink Floyd}
\zs
\Ch{Hm}{Hello}.

\Ch{Hm}{Is} there anybody\Ch{A}{ in} there? 

Just nod if you can \Ch{G}{hear} me\Ch{Em}{}

Is there \Ch{Hm}{anyone} home? 
\ks

\zs
Come on, now.

I hear you’re feeling down.

Well I can ease your pain,

Get you on your feet again.
\ks

\zs
Relax.

I need some information first.

Just the basic facts:

Can you show me where it hurts? 
\ks

\zr
\Ch{D}{There is} no pain, you are \Ch{A}{receding}.

\Ch{D}{A distant} ship’s smoke on the ho\Ch{A}{rizon.}

\Ch{C}{You are only} coming through in \Ch{G}{waves}.

\Ch{C}{Your lips} move but I can’t hear \Ch{G}{what} you’re sayin’.

\Ch{D}{When I was} a child I had\Ch{A}{ a} fever.

\Ch{D}{My hands} felt just like two ballo\Ch{A}{ons.}

\Ch{C}{Now I got} that feeling once aga\Ch{G}{in}.

I can’t explain, you would not under\Ch{C}{stand}.

This is not how I am\Ch{G}{.}

\Ch{A}{I} \Ch{G}{have} beco\Ch{D}{me comfortably} \Ch{A}{numb}.
\kr

\zs
Ok.
Just a little pinprick.

There’ll be no more --aaaaaahhhhh!

But you may feel a little sick.
\ks

\zs
Can you stand up? 

I do believe it’s working. good.

That’ll keep you going for the show.

Come on it’s time to go.
\ks

\zr
There is no pain, you are receding.

A distant ship’s smoke on the horizon.

You are only coming through in waves.

Your lips move but I can’t hear what you’re sayin’.

When I was a child I caught a fleeting glimpse,

Out of the corner of my eye.

I turned to look but it was gone.

I cannot put my finger on it now.

The child is grown, the dream is gone.

I have become comfortably numb.
\kr
\kp

